%% thesis.tex 2014/04/11
%
% Based on sample files of unknown authorship.
%
% The Current Maintainer of this work is Paul Vojta.

\documentclass[masters]{ucbthesis}
\usepackage{biblatex}
\usepackage{rotating} % provides sidewaystable and sidewaysfigure
\usepackage{float}
\usepackage{amsmath}
\usepackage[inkscapeformat=png]{svg}

% To compile this file, run "latex thesis", then "biber thesis"
% (or "bibtex thesis", if the output from latex asks for that instead),
% and then "latex thesis" (without the quotes in each case).

% Double spacing, if you want it.  Do not use for the final copy.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\addtolength{\abovecaptionskip}{\baselineskip}

\newtheorem{theorem}{Jibberish}

\bibliography{references}

\hyphenation{mar-gin-al-ia}
\hyphenation{bra-va-do}

\begin{document}

% Declarations for Front Matter

\title{Implementation of an Open-Source Generator for LPDDR4X Memory Controller}
\author{Reza Sajadiany}
\degreesemester{Spring}
\degreeyear{2023}
\degree{Master of Science}
\chair{Professor Borivoje Nikolic}
\othermembers{Professor Sophia Shao, Second Reader}
% For a co-chair who is subordinate to the \chair listed above
% \cochair{Professor Benedict Francis Pope}
% For two co-chairs of equal standing (do not use \chair with this one)
% \cochairs{Professor Richard Francis Sony}{Professor Benedict Francis Pope}
\numberofmembers{3}
% Previous degrees are no longer to be listed on the title page.
% \prevdegrees{B.A. (University of Northern South Dakota at Hoople) 1978 \\
%   M.S. (Ed's School of Quantum Mechanics and Muffler Repair) 1989}
\field{Electrical Engineering and Computer Science}
% Designated Emphasis -- this is optional, and rare
% \emphasis{Colloidal Telemetry}
% This is optional, and rare
% \jointinstitution{University of Western Maryland}
% This is optional (default is Berkeley)
% \campus{Berkeley}

% For a masters thesis, replace the above \documentclass line with
% \documentclass[masters]{ucbthesis}
% This affects the title and approval pages, which by default calls this
% document a "dissertation", not a "thesis".

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
\approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
\begin{center}
I dedicate this work to my parents who sacrificed many to give me the opportunity of a lifetime. 
\end{center}
\vfil\null
\end{dedication}

% You can delete the \clearpage lines if you don't want these to start on
% separate pages.

\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables

\begin{acknowledgements}

This project was conducted under the supervision and support of Professor Borivoje Nikolic and Sophia Shao at the UC Berkeley Slice lab and Berkeley Wireless Research Center.

I would like to acknowledge graduate student researcher Ken Ho who I worked with from the beginning phase of the project. The LPDDR4 project is a shared effort and work by Ken Ho and myself. The project will be maintained and further investigation in the area will continue by Ken Ho and other graduate and undergraduate students in the future. 

I acknowledge the help and support of Jennifer Zhou for keeping me on track during the course of my Master's degree.


I would like to acknowledge graduate student researchers at UC Berkeley's Slice lab and Berkeley Wireless Research Center namely Jerry Zhao, Vighnesh Iyer, Daniel Grubb, Harrison Liew, Abraham Gonzales, and Sagar Karandikar.

In this project, we referenced work done by Chipyard developers. I would like to thank the Chipyard development team and the Hammer development team.

Finally, I would like to acknowledge Apple for its generous assistance to my Master's degree by providing me with guidance, internship, and scholarship. 
\end{acknowledgements}

\end{frontmatter}

\pagestyle{headings}

% (Optional) \part{First Part}

\include{chap1}
\include{chap2}
\include{chap3}
\include{chap4}
\include{conclusion}

\printbibliography
\end{document}
